Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-30 data_appendix_all_years.Rmd
made a subset without the vacation kids

``` {r merging datasets}
total_data<- all_years %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary) %>%
  mutate(child = case_when(relation == 3 ~ 1,
                           relation != 3 ~ 0),
         grandchild = case_when(relation == 8 ~ 1,
                                relation != 8 ~ 0),
         pov_diff = income - pov_line,
         pov = case_when(pov_diff > 0 ~ 0,
                         pov_diff < 0 ~ 1),
         extr_diff = income - extr_pov,
         extr = case_when (extr_diff > 0 ~ 0,
                           extr_diff < 0 ~ 1),
                  work_reason = case_when(reason == "work" ~ 1,
                                 reason != "work" ~ 0),
         money_reason = case_when(reason == "money" ~ 1, 
                                  reason != "money" ~ 0),
         lny = log(income))

@@

#total <- total_children %>%
  #left_join(hh_head_2)
#left join command creating the duplicates problem it seems 
total <- merge(total_children,hh_head_2, by="hh_id")

total_subset <- total %>% distinct()

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

@@

probitMod_assist <- glm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data, family=binomial(link="probit"))  # build the logit model

summary(probitMod_assist)  # model summary
```

>>>>

``` {r merging datasets}
total_data<- all_years %>% 
  left_join(flood_summary) %>%
  left_join(drought_summary) %>%
  mutate(child = case_when(relation == 3 ~ 1,
                           relation != 3 ~ 0),
         grandchild = case_when(relation == 8 ~ 1,
                                relation != 8 ~ 0),
         pov_diff = income - pov_line,
         pov = case_when(pov_diff > 0 ~ 0,
                         pov_diff < 0 ~ 1),
         extr_diff = income - extr_pov,
         extr = case_when (extr_diff > 0 ~ 0,
                           extr_diff < 0 ~ 1),
                  work_reason = case_when(reason == "work" ~ 1,
                                 reason != "work" ~ 0),
         money_reason = case_when(reason == "money" ~ 1, 
                                  reason != "money" ~ 0))

@@

#total <- total_children %>%
  #left_join(hh_head_2)
#left join command creating the duplicates problem it seems 
total <- merge(total_children,total_heads_subset, by="hh_id")

#total_2 <- total[!(total$reason == "vacation" & total$assist == 0]

total %>%
  group_by(reason) %>%
  summarise(n = n())

total_2 <- subset(total, !(reason == "vacation" & assist == 0)) #taking out the observations with vacation kids

total_subset <- total_2 %>% distinct()

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         lny = log(income))

@@

probitMod_assist <- glm(assist ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_register <- glm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data, family=binomial(link="probit"))

probitMod_work <- glm(work_reason ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data, family=binomial(link="probit"))

summary(probitMod_assist)  # model summary
summary(probitMod_register)
summary(probitMod_work)
```
